Combining bottom up and top down approaches for Drug-Target-Interaction prediction

### 2019-12-09 presentations/2019-12-09/presentation.tex
Added presentation updates, ideas and TODO, Rerunning alignment for all drugs in DDI graph 1

		\footnotesize
		\def\arraystretch{1.2}
		\begin{tabular}{|r|r|r|r|r|r|r|r|}
			\hline
			\multicolumn{4}{|c|}{Used data}&layer sizes&model&Acc&AUC\\
			%\hline
			PPI&DDI&SE&HMM&&&&\\
			\hline
			1&1&0&0&641&graphsage&88.97&66.20\\
			1&1&0&0&641&graphsage&80.28&70.51\\
			1&1&0&0&641&graphsage&87.44&67.80\\
			1&1&0&0&641&graphsage&86.46&68.39\\
			1&1&0&0&641&graphsage&88.84&66.62\\
			1&1&1&0&641&graphsage&93.34&62.42\\
			1&1&1&0&641&graphsage&73.20&62.53\\
			1&1&1&0&641&graphsage&93.27&64.81\\
			1&1&1&0&641&graphsage&74.28&59.18\\
			1&1&1&0&641&graphsage&72.40&63.93\\
			1&1&1&0&641&gcn&88.61&67.27\\
			1&1&1&0&641&gat&82.65&71.69\\
			1&1&1&0&641&hinsage&83.18&70.33\\
			1&1&1&0&641&ppnp&89.80&67.78\\
			1&1&1&0&641&appnp&84.35&71.82\\
			1&1&1&0&641&sgc&86.50&68.45\\
			1&1&1&0&641&gcn&59.84&50.10\\
			1&1&1&0&641&gcn&97.11&56.02\\
			1&1&1&0&641&gat&59.77&50.06\\
			1&1&1&0&641&gat&55.48&55.93\\
			1&1&1&0&641&hinsage&59.77&50.06\\
			1&1&1&0&641&hinsage&94.06&63.52\\
			1&1&1&0&641&ppnp&21.54&50.15\\
			1&1&1&0&641&ppnp&77.98&55.85\\
			1&1&1&0&641&appnp&40.71&50.13\\
			1&1&1&0&641&sgc&2.27&50.18\\
			\hline  
		\end{tabular}
		\endgroup
	\end{figure}
\end{frame}

@@

>>>>

		\footnotesize
		\def\arraystretch{1.2}
		\begin{tabular}{|r|r|r|r|r|r|r|r|}
			\hline
			\multicolumn{4}{|c|}{Used data}&layer sizes&model&Acc&AUC\\
			%\hline
			PPI&DDI&SE&HMM&&&&\\
			\hline
			1&1&0&0&[32, 32]&graphsage&80.28&70.51\\
			1&1&0&0&[64]&hinsage&83.18&70.33\\
			1&1&0&0&[32, 64]&gcn&88.61&67.27\\
			1&1&0&0&[32, 64]&gat&82.65&71.69\\
			1&1&0&0&[64, 64, 128]&ppnp&89.80&67.78\\
			1&1&0&0&[64, 64, 128]&appnp&84.35&71.82\\

			\hline  
		\end{tabular}
		\endgroup
	\end{figure}
\end{frame}

		\footnotesize
		\def\arraystretch{1.2}
		\begin{tabular}{|r|r|r|r|r|r|r|r|}
			\hline
			\multicolumn{4}{|c|}{Used data}&layer sizes&model&Acc&AUC\\
			%\hline
			PPI&DDI&SE&HMM&&&&\\
			\hline
			1&1&1&0&[32, 64]&graphsage&93.27&64.81\\
			1&1&1&0&[64]&hinsage&94.06&63.52\\
			1&1&1&0&[32, 64]&gcn&97.11&56.02\\
			1&1&1&0&[32, 64]&gat&59.77&50.06\\
			1&1&1&0&[64, 64, 128]&ppnp&77.98&55.85\\
			1&1&1&0&[64, 64, 128]&appnp&94.43&66.43\\
			1&1&1&0&[64, 64, 128]&sgc&86.50&68.45\\
			1&0&1&0&[64]&hinsage&59.77&50.06\\
			1&0&1&0&[32, 64]&gcn&59.84&50.10\\
			1&0&1&0&[32, 64]&gat&55.48&55.93\\
			1&0&1&0&[64, 64, 128]&ppnp&21.54&50.15\\
			1&0&1&0&[64, 64, 128]&appnp&40.71&50.13\\
			1&0&1&0&[64, 64, 128]&sgc&2.27&50.18\\

			\hline  
		\end{tabular}
		\endgroup
	\end{figure}
\end{frame}

@@

\begin{frame}
	\begin{figure}
		\includegraphics[width=\linewidth]{../../models/graphsage_model.png}
		\caption{Graphsage model}
	\end{figure}
\end{frame}

\begin{frame}
	\begin{figure}
		\includegraphics[height=0.9\textheight]{../../models/hinsage_model.png}
		\caption{Hinsage model}
	\end{figure}
\end{frame}

\begin{frame}
	\begin{figure}
		\includegraphics[width=\linewidth]{../../models/gcn_model.png}
		\caption{GCN model}
	\end{figure}
\end{frame}

\begin{frame}
	\begin{figure}
		\includegraphics[width=\linewidth]{../../models/gat_model.png}
		\caption{GAT model}
	\end{figure}
\end{frame}

\begin{frame}
	\begin{figure}
		\includegraphics[height=0.9\textheight]{../../models/ppnp_model.png}
		\caption{PPNP model}
	\end{figure}
\end{frame}

\begin{frame}
	\begin{figure}
		\includegraphics[height=0.9\textheight]{../../models/appnp_model.png}
		\caption{APPNP model}
	\end{figure}
\end{frame}

\begin{frame}
	\begin{figure}
		\includegraphics[width=\linewidth]{../../models/sgc_model.png}
		\caption{SGC model}
	\end{figure}
\end{frame}

\begin{frame}
	\begin{figure}
		\includegraphics[height=0.9\textheight]{../../models/overall_model.png}
		\caption{Overall model}
	\end{figure}
\end{frame}
